%-------------------------
% Resume in Latex
% Author : Kenneth Assogba
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[utf8]{inputenc}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{blue}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://kennethassogba.co/}{\Large Kenneth Assogba}} & {\color{blue} Email} : \href{mailto: kenneth.assogba@etu.upmc.fr}{kenneth.assogba@etu.upmc.fr}\\
  %\href{https://kennethassogba.co/}{https://kenneth.assogba.co} & Mobile : 06 14 26 95 55 \\
  Internship in computational mechanics from April 1st, 2020 & {\color{blue} Mobile} : +33 6 14 26 95 55 \\
  {\color{blue} Github} : \href{https://github.com/kenn44}{https://github.com/kenn44} 
  %& 24 yo (12/02/1995)
\end{tabular*}


%-----------EDUCATION-----------------
\section{\color{blue}Education}
  \resumeSubHeadingListStart
    \resumeSubheading
    %Calcul Scientifique
      {Master 2 Mathematical Engineering - Numerical Analysis - Mechanics}{Paris, France}
      {\textbf{Sorbonne Université (former Université Pierre et Marie Curie)}}{Sept. 2019 -- Present}
    \resumeSubheading
      {MSc Fundamental Mathematics and Applications - PDE and Geometry}{Dangbo, Benin}
      {Institut de Mathematiques et de Sciences Physiques}{Oct. 2017 -- Aug. 2019}
    \resumeSubheading
      {Bachelor of Computer Science}{Cotonou, Benin}
      {École Superieure de Gestion d'Informatique et des Sciences}{Oct. 2016 -- Dec. 2017}
    \resumeSubheading
      {Bachelor of Mathematics}{Dangbo, Benin}
      {Institut de Mathematiques et de Sciences Physiques}{Oct. 2015 -- Jun. 2017}
    \resumeSubheading
      {Preparatory Classes in Mathematics and Physics}{Dangbo, Benin}
      {Institut de Mathématiques et de Sciences Physiques}{Oct. 2013 -- Jun. 2015}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{\color{blue}Experience}
  \resumeSubHeadingListStart
  
      \resumeSubheading
	  {Research Intern}{Dangbo, Benin}
	  {Research Unit in Mathematics and Mathematical Physics - IMSP}{May 2019 - Aug. 2019}
	  \resumeItemListStart
	  \item{Discrete monotonic schemes for the Schrödinger equation
	  \\\textbf{$\rhd$ \small{Literature review on Optimal Control in Quantum Mechanics
	  \\$\rhd$ Construction of implicit and explicit monotonic schemes
	  \\$\rhd$ Implementation of obtained algorithms and simulations with Octave}}}
	  \resumeItemListEnd
      
      \resumeSubheading
      {Co-lead}{Cotonou, Benin}
      {Python Benin User Group}{Dec. 2018 - Aug. 2019}
      \resumeItemListStart
        \resumeItem{\href{https://pythonbenin.com/}{pythonbenin.com}}
          {Organization of monthly meetings around Django, Flask, Tensorflow...}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
  
  
%--------PROGRAMMING SKILLS------------
\section{\color{blue}Computing skills and Languages}
\resumeSubHeadingListStart
 \item{
  	\textbf{Programming}{: Python, C++, Matlab, FreeFem++, Cuda, Code\_Aster,  Git, \LaTeX}
  }
\item{
	\textbf{Languages}{: English (Comprehension and writing of scientific texts), French(Native language)}
}
\resumeSubHeadingListEnd
  


%-----------PROJECTS-----------------
\section{\color{blue}Scientific Skills and Projects}
%$\rightarrow$ github.com/kenn44
%$\rhd$ Rapports et simulations
\resumeSubHeadingListStart
\resumeSubItem{Numerical optimization and simulation}

\resumeItemListStart
\item{Optimal control of Schrödinger equation with fixed step gradient algorithm and operator splitting method. Implementation and simulation with \textbf{Python}, NumPy et Matplotlib}

\item{Study of models in population dynamics including those of Lotka-Volterra and Verhulst. (Scilab)}

\item{Nonlinear optimization under constraints by SQP method (project: space launcher in Matlab)}      

\resumeItemListEnd


\resumeSubItem{Modeling and Numerical Analysis}

\resumeItemListStart
\item{Approaching the solution of a partial differential equation via \textbf{finite element} and \textbf{finite volume methods} - Solving an elliptic 2D problem in \textbf{C++}.}

\item{Writing of a Jupyter notebook presenting the main numerical methods of solving nonlinear equations $f(x)=0$ and their implementation in \textbf{Python}.}

\item{Python implementation of numerical methods for solving ordinary differential equations.}      

\resumeItemListEnd

  \resumeSubHeadingListEnd


\section{\color{blue}Interests}
  \resumeSubHeadingListStart
    %\item{\textbf{Anglais}{: Opérationnel}}
	
	\item{
	\textbf{Top Aéro }{(top-aero.com): Co-lead aeronautical pole of the association of aeronautics and aerospace of Sorbonne Université.}
	}
	\item{ \textbf{Space exploration} inhabited and uninhabited: Passionate, I followed the launches of Ariane 5, space shuttle Atlantis, the adventure of the probes Voyager 1 and 2.
	}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}\grid
\grid
