%-------------------------
% Resume in Latex
% Author : Kenneth Assogba
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://kennethassogba.co/}{\Large Kenneth Assogba}} & Email : \href{mailto: kennethassogba@gmail.com}{kennethassogba@gmail.com}\\
  \href{https://kennethassogba.co/}{https://kennethassogba.co} & Mobile : +229 67478728 \\
  Github : \href{https://github.com/kenn44}{https://github.com/kenn44} & 24 yo (February 12, 1995)
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Institut de Mathematiques et de Sciences Physiques (IMSP/UAC)}{Dangbo, Benin}
      {Master (2) of Science in Fundamental Mathematics and Applications}{Oct. 2018 -- Present}
    \resumeSubheading
      {Institut de Mathematiques et de Sciences Physiques (IMSP/UAC)}{Dangbo, Benin}
      {Master (1) of Science in Fundamental Mathematics and Applications}{Oct. 2017 -- Jun. 2018}
    \resumeSubheading
      {Ecole Superieure de Gestion d'Informatique et des Sciences (ESGIS)}{Cotonou, Benin}
      {Bachelor of Computer Science}{Oct. 2016 -- Dec. 2017}
    \resumeSubheading
      {Institut de Mathematiques et de Sciences Physiques (IMSP/UAC)}{Dangbo, Benin}
      {Bachelor of Mathematics}{Oct. 2015 -- Jun. 2017}
    \resumeSubheading
      {Institut de Mathematiques et de Sciences Physiques (IMSP/UAC)}{Dangbo, Benin}
      {Preparatory Classes in Mathematics and Physics (two-year highly selective classes)}{Oct. 2013 -- Jun. 2015}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Solutis \href{https://solutis-it.com/}{(solutis-it.com)} }{Cotonou, Benin}
      {Software Craftsman}{Oct 2017 - Present}
      \resumeItemListStart
        \resumeItem{SAC-TIC Project \href{https://sac-tic.tk/}{(sac-tic.tk)} \href{https://play.google.com/store/apps/details?id=com.solutis.sactic}{(Play Store)}}
          {SAC-TIC allows Beninese populations to be informed in case of break or disturbances of the water distribution network, to receive tricks and advices. Participation in frontend and server (NodeJS + PostgreSQL), development of the landing page, development of the bug notification form.}
        \resumeItem{\href{https://solutis-it.com/}{solutis-it.com}}
          {Design, build and deploy the company's website.}
      \resumeItemListEnd

    \resumeSubheading
      {EtriLabs \href{https://etrilabs.com/}{(etrilabs.com)}}{Cotonou, Benin}
      {Jr Software Engineer}{Apr 2017 - Sep 2017}
      \resumeItemListStart
        \resumeItem{Mongo Manager}
          {Allows to easily backup any mongodb database to a storage of your choice (AWS S3, Digital Ocean,..). Worked on the backend app with NodeJs and Express. \href{https://github.com/kenn44/mongo-manager}{Open Source repository}.}
%        \resumeItem{Nymeria}
%          {Development of a community marketplace for people to list, discover, and book unique accommodations online or from a mobile phone or tablet. \href{https://github.com/kenn44/marketplace-book-unique-accommodations}{Open Source repository}.}
      \resumeItemListEnd
      
      \resumeSubheading
      {Python Benin User Group [Community]}{Cotonou, Benin}
      {Co Organizer \href{https://pythonbenin.com/}{(pythonbenin.com)}}{December 2018 - Present}
 %     \resumeItemListStart
 %       \resumeItem{..Model..}
 %         {..Roadmap..}
 %     \resumeItemListEnd

    \resumeSubheading
      {Google Developer Group Porto-Novo [Community]}{Porto-Novo, Benin}
      {Co-lead \href{https://www.meetup.com/GDG-Porto-Novo/}{(meetup.com/GDG-Porto-Novo)}}{Jan 2018 - Jul 2019}
      \resumeItemListStart
	\resumeItem{Codelab: NodeJS Basics}
          {Introduction to NodeJS. \href{https://docs.google.com/presentation/d/1MmO1npyTXAGGuoSzTBCVJkYp5vT-VT3UkC4ul2a9RHI/edit?usp=sharing}{Presentation}.}
%        \resumeItem{Codelab: Tensorflow}
%          {Solve Real Problems with TensorFlow: From 0 to production ready app. \href{https://docs.google.com/presentation/d/1mA1svrJGFI6dQM-pmXnstHO20U28w70Qcd00fCanzFg/edit?usp=sharing}{Presentation}.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
      \resumeSubItem{Numerical analysis}
      {1. Root finding algorithms: Jupyter Notebook containing main numerical methods of solving non-linear equations $f(x)=0$. \href{https://github.com/kenn44/root-finding-algorithms}{Repository}. \\
      2. Numerical ODE: Numerical resolution of ordinary differential equations. \href{https://github.com/kenn44/numerical-ordinary-differential-equations}{Repository}.}
      \resumeSubItem{Optimal control and numerical optimization}
      {1. Modeling in population dynamics: We study four models including those of Lotka-Volterra and Verhulst. In each case we will do a balance point study and a numerical resolution with Scilab. \href{https://github.com/kenn44/modeling-in-population-dynamics}{Repository}. \\
      2. Optimal control of a Schrödinger type equation with the operator splitting and gradient descent methods. \href{https://github.com/kenn44/optimal-control-ode-splitting}{Repository}}
%    \resumeSubItem{AMMI Lightweight \href{https://suspicious-brown-5e9d1b.netlify.com/}{(Link)}}
%      {Rebuild of the the African Master of Machine Intelligence website (aims-ammi.com) to improve the rendering performance. Repository: \href{https://github.com/kenn44/ammi-lightweight}{--github.com/kenn44/ammi-lightweight-- .}}
    \resumeSubItem{Peekaboo (In progress) \href{https://play.google.com/store/apps/details?id=mvp.peekaboo.dev}{(Play Store)}}
      {A real time video chat dating app. In charge of the backend development and technical project lead, I faced several challenges: Setting up CI/CD pipeline to automate testing and deployment, implement realtime communication with WebSocket and WebRTC. I was able to work on new technologies such as Docker, Kubernetes and try new architectures: Serverless, GCP Compute Engine, AWS S3 (Cloud Storage).}
%    \resumeSubItem{Credit Scoring Model (Draft)}
%      {At OpenSI \href{http://opensi.co/}{(opensi.co)}, we start a project that aims to uses alternative data alongside of traditional to assess creditworthiness. The final goal is to improve the accessibility of persons excluded from banking institutions to credit. Notes available at \href{https://github.com/kenn44/credit-scoring101}{(github.com/kenn44/credit-scoring101)} }
%    \resumeSubItem{\href{blog.kennethassogba.co}{--blog.kennethassogba.co--} (In progress)}
%      {My personal blog.}
%    \resumeSubItem{InoTech (Closed) \href{https://inotech.ga/}{(inotech.ga)}}
%      {Ino-tech is an ambitious media founded in 2017 to study and show how technology impact our lives.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}\grid
\grid
